---
title: "Retweets Absolute Bulllisness Adjacency"
author: "Jonathan Bourne"
date: "23 February 2016"
output: html_document
---


```{r}
packages <- c("dplyr", "tidyr", "ggplot2", "caret", "corrplot", "xtable", "magrittr", "zoo", "igraph")
sapply(packages, library, character.only = TRUE)


basewd <- "C:/Users/Jonno/Dropbox/Data_Analytics" #change this to your dropbox file path for data analytics
DataFiles <- file.path(basewd, "Data")
GraphicsFiles <- file.path(basewd, "Graphics", "Milestone2")

```


Import data
```{r}
setwd(DataFiles)
TwitRetweets <- read.csv(gzfile("twitter_withretweets_daily.csv.gz"), as.is = TRUE)
symbology <- read.csv("symbology.csv")
setwd(GraphicsFiles)
```

#Data Preparation

Reshape the twitter data into wide form, remove weekends and holidays?
```{r}
TwitBull <- TwitRetweets %>% select(SYMBOL, TIMESTAMP_UTC, BULLISH_INTENSITY) %>% 
  spread(key = SYMBOL, value = BULLISH_INTENSITY, fill = 0) #change metric
setwd(DataFiles)

```


Remove variables of near zero variance. Save as csv
```{r}
x1 <-nearZeroVar(TwitBull)
TwitBullvar <- TwitBull[,-x1]
#write.csv(TwitBull, file = "TwitBullWide.csv") #save under new type with correct metric

```


Seperate into time periods and create a single test time period
```{r}

```

Decompose to enforce stationarity in each timeseries, this will create a large list of decomposed data
```{r}

```

Create distance matrix
```{r}

```

Create Adjacency matrix 
```{r}

```

Merge Distance and Adjacency matrices to create a weighted undirected graph
```{r}

```

Structure graph for use in gephi with as much metadata as possible
symbol, cluster ID, edge type (aka inter cluster vs intra cluster), is target symbol/node yesy/no etc
```{r}

```

